What's in a Name? Linear Temporal Logic Literally Represents Time Lines

### 2023-01-01 paper/main.tex
tikz fig 6

\usepackage{amsmath, amssymb, amsthm,tikz}
\usetikzlibrary{positioning,shapes,quotes}

@@

\subsection{$\omega$-regex to timeline} \label{regex2timeline}
Our tool uses Graphviz~\cite{Ellson2001GraphvizO} to achieve the timeline visualization step. By construction of our algorithm, every $\omega$-regular expression is in the form of
\[
    A_1A_2^{\omega} + A_3A_4^{\omega} + \cdots + A_{2n-1}A_{2n}^{\omega}
\]
where $A_i$ are regular expressions, and $A_{2i-1}$ could be $\epsilon$. On a high level, for each of regular expression $A_i$, we visualize it as a set of accepted input. We view each union operator as parallel timelines, and each $A_{2i-1}$ is concatenated with $A_{2i}$ repeated infinitely many times, as represented in the grey box. \cref{fig:timeline} presents a generic timeline resulting from this form of construction.
\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.5]{img/timeline.png}
    \caption{Generic timeline construction from $A_1A_2^{\omega} + A_3A_4^{\omega} + \cdots + A_{2n-1}A_{2n}^{\omega}$}
    \label{fig:timeline}
\end{figure}

>>>>

\usepackage{amsmath, amssymb, amsthm,tikz}
\usetikzlibrary{positioning,shapes,quotes,calc}

@@

\subsection{$\omega$-regex to timeline} \label{regex2timeline}
Our tool uses Graphviz~\cite{Ellson2001GraphvizO} to achieve the timeline visualization step. By construction of our algorithm, every $\omega$-regular expression is in the form of
\[
    A_1A_2^{\omega} + A_3A_4^{\omega} + \cdots + A_{2n-1}A_{2n}^{\omega}
\]
where $A_i$ are regular expressions, and $A_{2i-1}$ could be $\epsilon$. On a high level, for each of regular expression $A_i$, we visualize it as a set of accepted input. We view each union operator as parallel timelines, and each $A_{2i-1}$ is concatenated with $A_{2i}$ repeated infinitely many times, as represented in the grey box. \cref{fig:timeline} presents a generic timeline resulting from this form of construction.
\begin{figure}[h!]
    \centering
    \begin{tikzpicture}
    \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a1) {$A_1$};
    \node[shape=rectangle, fill=gray!30!white, style={minimum width=1.8cm, minimum height=1.3cm}] (a2g) [right= 0.85cm of a1] {};
    \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a2) [right= 1cm of a1] {$A_2$};
    \node[draw, thick, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a3) [below= 0.4cm of a1] {$A_3$};
    \node[shape=rectangle, fill=gray!30!white, style={minimum width=1.8cm, minimum height=1.3cm}] (a4g) [right= 0.85cm of a3] {};
    \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a4) [right= 1cm of a3] {$A_4$};
    \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a5) [below= 0.4cm of a3] {...};
    \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a7) [below= 0.4cm of a5] {\!\!\!$A_{2n-1}$\!\!\!};
    \node[shape=rectangle, fill=gray!30!white, style={minimum width=1.8cm, minimum height=1.3cm}] (a8g) [right= 0.85cm of a7] {};
    \node[fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (a8) [right= 1cm of a7] {\!\!\!$A_{2n}$\!\!\!};
    \node (m) at ($(a1)!0.5!(a7)$) {};
    \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (s) [left= 1.5cm of m] {\!\!\!\!start\!\!\!\!};
    \draw[thick] (s) edge[-latex] (a1) (s) edge[-latex] (a3) (s) edge[-latex] (a5) (s) edge[-latex] (a7);
    \draw[thick] (a1) edge[-latex] (a2) (a3) edge[-latex] (a4) (a7) edge[-latex] (a8);
    \end{tikzpicture}
%    \includegraphics[scale=0.5]{img/timeline.png}
    \caption{Generic timeline construction from $A_1A_2^{\omega} + A_3A_4^{\omega} + \cdots + A_{2n-1}A_{2n}^{\omega}$}
    \label{fig:timeline}
\end{figure}
